Comments on binomial graph learning

### 2022-04-19 model specification.Rmd
add poster and fix model specification

where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at round or stratum $j$. In the following, we will use

@@

### Conditional likelihoood function
The conditional likelihood function for all strata is written as
\begin{equation}
	\label{eq:conlikelihood}
	\begin{aligned}
	&	L(\mathbf{A}, \beta)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
	\end{aligned}
\end{equation}

@@

\begin{equation}
	\label{eq:condloglikelihood}
	\begin{aligned}
	&	\text{log}(L(\mathbf{A}, \beta))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) ,
	\end{aligned}
\end{equation}

>>>>

where $\mathbf{A}$ is the adjacency matrix from the graph $G$, $h$ is a vector of latent factors that governs $p_{i, j}$ through $\mathbf{A}$ and assumed to be a standard normal random vector, and $\alpha_j$ is a round specific parameter at round or stratum $j$, and assumed to be normally distributed with mean of 0, and unknown variance $\sigma^2$

@@

### Conditional likelihoood function
The conditional likelihood function for all strata is written as
\begin{equation}
	\label{eq:conlikelihood}
	\begin{aligned}
	&	L(\mathbf{A}, h)  = \prod_{j=1}^M {\text{exp} (\sum_{l \in O_j}\mathbf{A}[l, ] h ) \over \sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) },
	\end{aligned}
\end{equation}

@@

\begin{equation}
	\label{eq:condloglikelihood}
	\begin{aligned}
	&	\text{log}(L(\mathbf{A}, h))  = \sum_{j=1}^M \sum_{l \in O_j}\mathbf{A}[l, ] h  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h ) 
	& = \sum_{j=1}^M \mathbf{A} h y_j  - \sum_{j=1}^M \text{log}\sum_{J \in C_{k_j}^N} \text{exp} (\sum_{a \in J}\mathbf{A}[a, ] h )
	\end{aligned}
\end{equation}

### The Estimator
The maximum likelihood estimator is then defined as $\mathbf{A}$ which maximize (\ref{eq:condloglikelihood}), which is equivalent to minimizing the negative conditional log likelihood.
